To establish knowledge about the domain and issues with the current system for managing meeting arrangements, two interviews with the stakeholders was conducted.  
The goals of these interviews were twofold: 
First and foremost, we wanted  to understand the current issues the stakeholders are facing. 
To figure this out we conducted an unstructured interview\cite{robson2002real}.
Secondly, we wanted to understand what the stakeholder sees as minimum requirements for a potential solution to their problem through an interview.
This interview was based on ideas provided to us by the stakeholder during the initial contact.
Due to not knowing the specifics about the problem, we could not create close-ended questions for a structured interview, and thus chose to use a semi structured interview focusing on open-ended questions. This allowed us to ask complementary questions to clarify answers \cite{InterviewsNHS}.


\section{Understanding the problem} % What constitutes a solution for 
During the initial interview, the stakeholders provided us with insight into what their current needs are, and why their current system does not satisfy these needs.
First and foremost, the stakeholder have issues with arranging meetings throughout their day to day life.
When employees of Mariendal IT schedues meetings they sometimes experience problems with not having available rooms.
The unavailability is often due to the meeting organizer not registering that a meeting has concluded early.
This leads to meeting rooms being unattended while still being marked as in-use in their calendar system.
Furthermore, the stakeholder will sometimes have unscheduled visits from clients, and will thus need a place discuss business impromptu.
Secondly, registering new meetings requires the user to use their computer and open propriatery software to schedule the the meeting and reserve a room. Making changes to an existing meetins, such as extending the duration of the meeting, can only be done by finding the meeting in their current system, and edit the details of the meeting.
This makes it tedious and time-consuming to extend meetings, as the organizer has to leave the room to find a computer and register the changes. 
Thirdly, making arrangements other than reserving rooms can be time consuming and annoying. 
It is sometimes necessary to bring IT equipment to meetings to showcase them for customers.
This means that it is necessary to plan and coordinate where and when equipment is in use to ensure that the it is available for meetings. 
Similarly, it is customary to provide refreshments and snacks during the meeting, which must also be arranged. 
Currently, this is done by reaching out to the cafeteria via phone or email.
This adds yet another task that needs to be solved to accomodate meetings. 

In summary, the current system used by the stakeholder is inefficient as it is unflexible and does not integrate with their other workflows. 

%Understanding the problem and problem analysis
%What issues are they facing --> usability and integration with their current system

\section{Requirements}\label{sec:requirement_elicitation}
Having gained an understanding of the stakeholders' problems and the domain in which they recide, we could refine the initial ideas provided to us at first contact with the stakeholder.
We refined the ideas into user stories in collaboration with the stakeholder.%HOW????
These user stories were prioritized further using MoSCoW analysis\cite{DEBbook}.
A MoSCoW prioritization is a rough prioritization into four categories based on an agreement between stakeholders and the developers.
Each category describes a prioritization level of particular user stories. The four categories are as follows: \textit{Must have}, \textit{Should have}, \textit{Could have}, \textit{Wont have}.

% \begin{table}[]
%     \begin{tabular}{|l|}
%     \hline
%     \textbf{Must Have}                                                                                                                                                                                                                                                                       \\ \hline
%     As a user, I want to be able to book a meeting room through Outlook/Outlook mobile and select it as a location, so that I can easily schedule my meetings and reserve a space                                                                                                            \\ \hline
%     As a user, I want to be able to book a meeting room through a website and view it in Outlook afterward, so that I can use the platform that is most convenient for me.                                                                                                                   \\ \hline
%     As a user, I want to be able to see who has booked a meeting room, so that I can avoid scheduling conflicts and ensure that the room is available when I need it.                                                                                                                        \\ \hline
%     As a user, I want there to be a screen at each meeting room displaying the name of the person who has booked it (without meeting details), and the ability to book the room immediately for an upcoming meeting.                                                                         \\ \hline
%     As a user, I want the platform to use MFA login for both users and the admin page, to ensure that only authorized individuals can access and use the system.                                                                                                                             \\ \hline
%     As an administrator, I want to be able to create multiple customers, each with their own unique administration flow, so that I can set up and manage multiple organizations within a single solution                                                                                     \\ \hline
%     \textbf{Should Have}                                                                                                                                                                                                                                                                     \\ \hline
%     As a user, I want to be able to end a meeting early on the screen, so that I can free up the meeting room for another user                                                                                                                                                               \\ \hline
%     As a user, I want to be able to create a meeting room in the administration section and have it automatically created in Exchange Online, so that I can manage the process from a central location and avoid duplication of effort                                                       \\ \hline
%     As a user, I want to be able to customize the application deployment to feature branding such as a custom logo. This enables me to personalize the platform and align it with my company's branding                                                                                      \\ \hline
%     As a user, I want to be able to send reminders to attendees via email, so that I can ensure that they are aware of the meeting and arrive on time                                                                                                                                        \\ \hline
%     As a user, I want to be able to view an overview of available meeting rooms, such as a floor plan or other layout, on a large screen, so that I can quickly and easily find an appropriate space for my meeting                                                                          \\ \hline
%     \textbf{Could Have}                                                                                                                                                                                                                                                                      \\ \hline
%     As a user, I want to be able to display an info screen if there are no meetings scheduled, until a certain time before the next meeting. This would allow me to use the meeting room for other purposes, such as advertisements or presentations, when it is not being used for meetings \\ \hline
%     \textbf{Won’t Have}                                                                                                                                                                                                                                                                      \\ \hline
%     As a user, I want to be able to order catering, such as coffee, bread, and lunch, and send an email to the canteen, so that I can easily provide refreshments for my meeting attendees                                                                                                   \\ \hline
%     As a user, I want to be able to order equipment, such as a projector or whiteboard, so that I can make sure that the meeting has the necessary tools to be successful                                                                                                                    \\ \hline
%     \end{tabular}
%     \end{table}
%what the benefits of user stories are
\subsection*{Must have}
\begin{enumerate}
\item As a user, I want to be able to book a meeting room through Outlook/Outlook mobile and select it as a location, so that I can easily schedule my meetings and reserve a space.
\item As a user, I want to be able to book a meeting room through a website and view it in Outlook afterward, so that I can use the platform that is most convenient for me.
\item As a user, I want to be able to see who has booked a meeting room, so that I can avoid scheduling conflicts and ensure that the room is available when I need it.
\item As a user, I want there to be a screen at each meeting room displaying the name of the person who has booked it (without meeting details), and the ability to book the room immediately for an upcoming meeting.
\item As a user, I want the platform to use MFA login for both users and the admin page, to ensure that only authorized individuals can access and use the system.
\item As an administrator, I want to be able to create multiple customers, each with their own unique administration flow, so that I can set up and manage multiple organizations within a single solution. % In the context of the Microsoft ecosystem, this would correspond to multiple tenants.
\end{enumerate}


\subsection*{Should have}
\begin{enumerate}
\setcounter{enumi}{6}
\item As a user, I want to be able to end a meeting early on the screen, so that I can free up the meeting room for another user.
\item As a user, I want to be able to create a meeting room in the administration section and have it automatically created in Exchange Online, so that I can manage the process from a central location and avoid duplication of effort.
\item As a user, I want to be able to customize the application deployment to feature branding such as a custom logo. This enables me to personalize the platform and align it with my company's branding.
\item As a user, I want to be able to send reminders to attendees via email, so that I can ensure that they are aware of the meeting and arrive on time.
\item As a user, I want to be able to view an overview of available meeting rooms, such as a floor plan or other layout, on a large screen, so that I can quickly and easily find an appropriate space for my meeting.
\end{enumerate}

\subsection*{Could have}
\begin{enumerate}
\setcounter{enumi}{11}
\item As a user, I want to be able to display an info screen if there are no meetings scheduled, until a certain time before the next meeting. This would allow me to use the meeting room for other purposes, such as advertisements or presentations, when it is not being used for meetings.
\end{enumerate}

\subsection*{Nice to have}
\begin{enumerate}
\setcounter{enumi}{12}
\item As a user, I want to be able to order catering, such as coffee, bread, and lunch, and send an email to the canteen, so that I can easily provide refreshments for my meeting attendees.
\item As a user, I want to be able to order equipment, such as a projector or whiteboard, so that I can make sure that the meeting has the necessary tools to be successful.
\end{enumerate}

After performing the MoSCoW analysis and documenting the results, the derived user stories and their priority was sent to the stakeholder for feedback and to confirm mutual understanding.

\subsection{Existing solutions}
