\section{Designing a product} % generel hci
When establishing a design for a product, one often begins with exploring initial thoughts and ideas for a design, only to then present the design to the user, make adjustments, and repeat the process. 
This can be described in a process called the design funnel.\cite{BUXTON2007135_skething}

Buxton\cite{BUXTON2007135_skething,BUXTON2007139_prototyping} describes how to move from an exploratory analysis of different designs through sketching to interactive, product refinement using prototypes. 
Sketching is the act of ideation and capturing key concepts of the design in a cheap and easy-to-make artifact. 
It is important to notice that the artifact itself is but a byproduct of the process, while the goal of the activity lies within the process itself.\cite{BUXTON2007135_skething}
The true goal is to understand user needs and develop a design concept that both the designer and user find agreeable in terms of requirements and user experience. 
When sketching, one must put aside assumptions and preconceptions about the product one is designing.
This helps the designer discover new ideas for the product due to not being constrained by an existing understanding of requirements, user needs, and expert knowledge. %kilde? 
Sketching techniques often include the participation of users of the developing product.
This helps the designer focus efforts on designing a system that suits the user and fulfills their needs.
This is known as user-centered design (UCD). \cite{user-centred-design}
Techniques within UCD include user sketching, prototype evaluation, and usability experiments involving users.

In the following sections, this report details techniques for creating a prototype, and how such a prototype can be used when performing a usability evaluation.