\section{Environmental systems}\label{sec:presence_env}
Environmental systems for occupancy detection leverage a variety of sensors that measure physical attributes of an environment, such as carbon dioxide ($\text{CO}_{2}$) concentration, temperature, humidity, and infrared radiation.
These systems infer occupancy by detecting changes in environmental parameters caused by human presence.
For instance, an increase in $\text{CO}_{2}$ levels may indicate occupancy due to human respiration.\cite{longoAccurateOccupancyEstimation2019}
\input{problem_analysis/presence/environmental.tex}

\section{Video-based systems}\label{sec:presence_video}
Video-based systems for occupancy detection utilize various imaging technologies and techniques to identify the presence of people within a specified area. 
These system uses the adaptability of cameras to capture visual data, that can be used detect motion using approaches like machine learning. 
These approaches allow video-based systems to accurately estimate the number of people in a monitored space.
In the following section, we examine the use of video-based technologies for presence detction, discussing the advantages and disadvanteges with various methods.
\input{presence/video_based_detection.tex}

\section{Radio-based systems}\label{sec:presence_radio}
Radio-based occupancy detection systems make use of wireless communication technologies, such as Wi-Fi and Bluetooth, to determine the presence of individuals in a given area.
These systems exploit the fact that most people carry devices that emit wireless signals like smartphones and wearables.

By monitoring the strength and distribution of these signals, radio-based systems can infer the number of occupants and their locations within the monitored area.\cite{longoAccurateOccupancyEstimation2019, teissedre-2019}
