\section{Implementing Agile Project Management with Scrum}
Developing a software product for a business can be a complex process.
Incremental agile approaches have become popular to address this complexity, as it allows for fast adaptation to changes in user needs. \cite{sommervilleSoftwareEngineering2016}
In incremental-agile approaches, system development is considered a series of increments, each adding functionality to the system.
Between these increments, one gathers feedback from stakeholders to prioritize functionality for the next increment.
Therefore, each increment adds value to the user.
By continuously getting feedback and working with these increments, the development process becomes cheaper and faster as less time is spent adapting to changes.\cite{sommervilleSoftwareEngineering2016}
This section will discuss how an agile approach has been utilized in this project. 

\subsection{Scrum Framework}
Agile is a set of values and does not present practical activities which a process model would consist of\cite{sutherlandScrumArtDoing2014}.
Therefore, the team has decided on the agile framework Scrum\cite{scrumdotorg}. Scrum chosen as it puts the values to practice and due to prior experience with using the framework amongst team members. \todo{What does it mean to put the values to practice}

Scrum introduces a number of practices and roles, which is described in the following sections. 

\subsubsection*{Roles and Responsibilities}
A Scrum team consists of three roles: the Scrum Master, a Product Owner, and developers.
The Scrum Master is responsible for enforcing scrum and helping the team remain productive.
Their goal is to guide the team towards continuous improvement.
A Product Owner is responsible for maximizing the value of the product.
They are also accountable for managing the product backlog, which involves developing a product goal, creating backlog items, prioritizing these items, and ensure the team understands the items. \cite{scrumdotorg}

\subsubsection*{Artifacts and Tools}
Scrum offer a number of artifacts and tools to help ensure the project is organized, focused, and continuously improving. These include, but are not limited to, the product backlog, user stories, sprints, sprint backlog, sprint goal, increments, definition of done, daily scrums, sprint review, and sprint retrospective.\cite{sutherlandScrumArtDoing2014}

The \textbf{product backlog} is a list of user stories, and represents every possible addition to the project.
Due to the comprehensive nature of this list, it is not possible to build everything.
Therefore, the list should be prioritized by what delivers the most value to users.
Backlog items then are estimated by the team in terms of relative size.
A common measure for estimation is the Fibonacci sequence.
As the stakeholders provide feedback, items in the backlog should be prioritized accordingly.
All these items contribute to achieving the \textbf{product goal}.
The backlog items are \textbf{user stories}.

User stories represent functionality the stakeholder would like to see in the system.
For this reason, they must include \textit{who} it is for, \textit{what} should be done, and \textit{why} they want it.
This is captured in the general "\texttt{As a X, I want Y, such that Z.}" format for user stories.
A \textbf{sprint} is a short period of time, during which the team works on a subset of the product backlog, captured in a \textbf{sprint backlog}.
This defines the \textit{what} of the sprint.
The items in the sprint backlog are chosen based on a \textbf{sprint goal}, defining the \textit{why} of the sprint.


The sprint has an actionable plan for delivering the increment, representing the \textit{how}. \todo{what is how? It is not mentioned anywhere else.}
At the beginning of teach sprint, the Scrum team performs \textbf{sprint planning}.
Here, the team discuss and choose the most important backlog items for the sprint.
Then they find a \textbf{sprint goal} which clarifies why the sprint is valuable to the users.
The team also discussed how the chosen work will get done in increments that meet the definition of done.
\textbf{Increments} can be viewed as stepping stones toward the product goal.

Each results in a product that is closer to reaching the product goal.
A \textbf{definition of done} describes the minimum requirements that must be fulfilled before an increment can be considered completed.
Usually, simply implementing a feature is not sufficient to meet this definition.
Testing, ensuring deployability, and writing documentation may also be required.
As the sprint progresses, the team hold \textbf{daily scrums}, which are short meetings where the team inspects progress towards the sprint goal and adjust the sprint backlog as necessary.
Daily scrums are meetings where progress towards the sprint goal is discussed.
Each increment will be inspected during \textbf{sprint review}.
During such a review, progress is examined, the team and its stakeholders discuss any changes, and then figure out what to do next.

Finally, the team conducts a \textbf{sprint retrospective}, where the team examines how their last sprint went, and how they may improve.
This is part of the quest for continuous improvement.\cite{sutherlandScrumArtDoing2014}

In summary, Scrum involves repeatedly taking backlog items and working on them during a sprint.
After each sprint, the team and stakeholders inspect the results and adjust for the next sprint.
This fosters continuous improvement by getting rapid feedback on work.
Our team has chosen to work in three-week sprints.
This will allow us enough time to develop useful functionality of meaningful sizes but does not limit us in terms of adaptability.
The team's will include two definitions of done - one for deciding when a user story is satisfied and one for deciding when subtasks of the users stories are done.
\begin{dod}
    For a user story to be complete two requirements must be satisfied: An end-to-end test must carried out to ensure that the functionality needed to satisfy the user story is completed. Secondly, the implementation of the user story must be documented. 
\end{dod}
To ensure that the definition of done for user stories are satisfied each story has an owner. 
The owner must ensure that the definition of done is satisfied before the future is deemed complete.

For minor tasks the following the definition of definition of done is used. 
\begin{dod}
    All written code must be annotated with types and a linter used to ensure the quality of the code.
    Before any code is merged into the existing code base using version control, it must be tested that the system compiles and build successfully.  
\end{dod}

In the next section, we will describe how we gathered initial requirements for the project and created user stories for the product backlog.