% Describes the premise of the project. That we collaborate and they come with requirements and what they want overall. 
% Hvordan vil vi samarbejde med dem
% Hvad skal de få ud af samarbejdet
This project is made in collaboration with Mariendal IT, who has acted as the stakeholder in this project.
They specialize in IT and offer services such as hosting, security, and operations management\cite{Mariendal_OmOs}.
Henceforth, Mariendal IT and its constituents will be referred to as the stakeholder. 
As a stakeholder, they provided insight towards their perceived requirements, performed prototype- and UI evaluation, and feedback regarding the developed product, by attending meetings and interviews with us.
This is detailed through a problem analysis using techniques from user centred design leading into the development of a prototype used to establish the problem formulation. 
Furthermore, this project regards itself with the design and evaluation of a presence detection system used to establish whether a meeting room is occupied.
Presence systems utilize different technologies and approaches to establish location of nearby people or devices.
A technology has been picked based on the following criteria: accuracy and precision of location determination, how easily these are affected by the environment, as well as privacy considerations and cost of implementation.
Thereafter, methods and techniques for presence detection using Bluetooth Low Energy are presented, followed by the selection of a method appropriate for this project. 
In this regard, fingerprinting using a kNN approach is found suitable.  
Lastly, the system is examined by evaluating how well it determines whether a meeting room is occupied.
%their problem


% hvad omhandler det?
% hvad bruger de nu?
% hvordan lever det ikke op til deres krav
% hvordan kan det forbedres

%Our stakeholders problem, was that their current system, did not have sufficient support for on-site arrangement of meetings.
%Currently, stakeholders have to interact with multiple system interfaces, to accomodate all of their needs when arranging meetings on-site. 
%These interactions are cumbersome, which is not ideal for a work environment.
