\section{Fingerprinting}
Fingerprinting is a technique utilizing the measured power of the received Bluetooth signal to accommodate the physical layout of the room in which the system is deployed. 
Setting up a system utilizing fingerprinting requires two phases: a phase where the layout of the room is analysed to accommodate the impact of physical obstacles in the room, and a phase where the unknown position of a Bluetooth receiver is inferred \cite{presence_ble_review, taking_localization_to_the_wild}. Often, this map is used to create machine-learning models \cite{taking_localization_to_the_wild}.

\citeauthor{taking_localization_to_the_wild} \cite{taking_localization_to_the_wild} presents results for a fingerprinting approach using random forest regression.
They show how varying measured RSSI across devices can be mitigated by using RSSI differences between pairs of beacons.
They conclude that maps created by the measuring device in the first phase can be reused to create maps for other types of devices without significant loss of accuracy. 
\citeauthor{presence_ble_review}\cite{presence_ble_review} presents several ways to use the map to create models for fingerprinting, but does not evaluate them.
\citeauthor{improving_indoor_localization} \cite{improving_indoor_localization} choose to use a K-nearest neighbour directly on the observed data and compute the average location between the selected k neighbours and the actual position. 
Their experiments are performed in an area of 52x43 meters using 17 BLE beacons.
The experiment yields accurate results, although with a few drastic outliers. 
They conclude that the number of beacons greatly affects the accuracy of the approach. 


